---
title: "Adidas"
output: html_document
date: "2022-10-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Loading the packages
library(ggplot2)
library(dplyr)
library(corrplot)
library(Rmisc)
library(ragtop)
library(readxl)
library(fastDummies)
library(class)
library(glmnet)
library(ranger)
library(caTools)
library(vip)
library(devtools)
library(usdata)
library(usmap)
library(maps)
library(tidyverse)
library(urbnmapr)
library(mapview)
library(ggmap)
library(RColorBrewer)
```



```{r}
adidas <- read.csv(file.choose(), header = TRUE)
summary(adidas)

```

Data Cleaning - exclude things unrealted: url, sku, original_price, availability(all of the products are in stock), currency(all products are in USD), source(All come from same source), source_website, brand, country, language
```{r}
drop <- c("url","sku","original_price","currency", "availability", "source", "source_website", "brand", "country", "language", "images", "crawled_at", "description", "name", "breadcrumbs", "index")
adidas2 <- adidas[,!(names(adidas) %in% drop)]

charV <- which(sapply(adidas2, is.character))
charVnames <- names(charV)
length(charVnames) 
numV <- which(sapply(adidas2, is.numeric))
length(numV) 

#change categorical variables into factors
for (i in 1:length(charVnames)) {
      adidas2[,charV[i]] = as.factor(adidas2[,charV[i]])
}


#creating dummy variables
adidas_dum <- dummy_cols(adidas2, remove_first_dummy = TRUE)
adidas_dum <- adidas_dum %>%
      select(-charVnames)

#creating interaction
X <- model.matrix (selling_price ~ (.)*category -1, data = adidas2)
X <- cbind("selling_price" = adidas2$selling_price, X)

summary(X)
```

correlations between variables
```{r}
corAll <- cor(X, use = "pairwise.complete.obs")
corAll_sort <- as.matrix(sort(corAll[,'selling_price'], decreasing = TRUE))
corAll_high <- names(which(apply(corAll_sort, 1, function(x) abs(x)>0.3)))
corAll_high

corAll1 <- corAll[corAll_high,corAll_high]
corrplot.mixed(corAll1, tl.col="black", tl.pos = "lt", number.cex = 0.7)
```

density plot of selling price for each color
```{r}
Col <- adidas2 %>%
      group_by(color) %>%
      summarize_at(vars(selling_price), list(avgprice = mean))

ggplot(Col, aes(x = color, y = avgprice, fill = color)) +
  geom_col()+
  scale_fill_manual(values = c("gray","gray","gray","red","yellow","yellow","gray","gray","gray","yellow","gray","gray","gray","gray","red","red","gray","gray")) +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
ggplot(adidas2, aes(x = color, fill = category)) +
      geom_bar(position = "fill") + 
      theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))

Cat <- adidas2 %>%
      group_by(category) %>%
      summarize_at(vars(selling_price), list(avgprice = mean))
ggplot(Cat, aes(x = category, y = avgprice)) +
      geom_col() +
      theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))

ggplot(adidas2, aes(x = selling_price, color = category)) +
      geom_density()
```

Accessories
```{r}
ColAcc <- adidas2 %>%
      filter(category == "Accessories") %>%
      group_by(color) %>%
      summarize_at(vars(selling_price), list(avgprice = mean))
ggplot(ColAcc, aes(x = color, y = avgprice)) +
      geom_col() +
      theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
```


Clothing
```{r}
ColClo <- adidas2 %>%
      filter(category == "Clothing") %>%
      group_by(color) %>%
      summarize_at(vars(selling_price), list(avgprice = mean))
ggplot(ColClo, aes(x = color, y = avgprice)) +
      geom_col() +
      theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
```


Shoes
```{r}
ColShoes <- adidas2 %>%
      filter(category == "Shoes") %>%
      group_by(color) %>%
      summarize_at(vars(selling_price), list(avgprice = mean))
ggplot(ColShoes, aes(x = color, y = avgprice)) +
      geom_col() +
      theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
```



density plot across all inputs with median
```{r}
medianSit <- median(adidas2$selling_price) #store median
ggplot(adidas2, aes(x = selling_price)) +
      geom_density() +
      geom_vline(xintercept = medianSit, size = 1, color = "red") +
      geom_text(aes(x = medianSit + 5, label = paste0("median\n", medianSit), y = 5e-04)) 

ggplot(adidas, aes(x= selling_price, y = average_rating)) +
      geom_point(alpha = 0.2) +
      geom_jitter() +
      facet_wrap(~ category)
```


